Modal Abstractions for Virtualizing Memory Addresses

### 2023-02-27 programlogic.tex
synch
+

    \[ \nfpointsto{\mask\vaddr\ft\crthree}{\mask\vaddr\tw\crthree}\entryf\qfracfotsss\naddr \]

@@

    \[ \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qfracfotss\naddr \]

@@

    \[ \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qfracfots\naddr \]

@@

    \[ \nfpointsto{\mask\vaddr\ft\entrytw}{\mask\vaddr\tw\entrytw}\entryo\qfracfot\naddr \]

@@

    \[ \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr \]
\end{itemize}
\begin{remark}[A Strong Definition for Virtual Memory Addressing]
  \label{rem:strongvmem}

\begin{figure*}
\[
\begin{array}{l}
  \ppointsto\vaddr\locsf\vpts \stackrel{def}{=} \lambda \tlf\Loc.\\
  \exists_{\tlfoff\Locn \;, \tltoff\Locn \;, \tltwoff\Locn \;,\tlooff\Locn \;, \tpgoff\Loctw \;, \tlt\Loc \;, \tltw\Loc \;, \tlo\Loc \tpg\Loc} \ldotp \\
  \ulcorner \textsf{aligned } \vaddr \urcorner \star 
   \ulcorner \vaddr = \locsx :: \lfoff :: \ltoff :: 
   \ltwoff :: \looff :: \pgoff \urcorner \star\\
  \pfpointsto{\lvlsum\crt\lfoff}{\lvlbor\lt}\qfracfotsss\ppts \star 
  \pfpointsto{\lvlsum\lt\ltoff}{\lvlbor\ltw}\qfracfotss\ppts \star \\
  \pfpointsto{\lvlsum\ltw\ltwoff}{\lvlbor\lo}\qfracfots\ppts \star 
  \pfpointsto{\lvlsum\lo\looff}{\lvlbor\pg}\qfracfot\ppts \star \\
  \ppointsto{\pageptstosum\pg\pgoff}\locsf\ppts 
\end{array}
\]
\caption{A Strong Virtual Points-to Relation}
\todo[inline]{These fractions aren't quite right (though I see you added the variance between levels), I can walk you through in our meeting tomorrow.}
  \label{fig:strongvirtualpointsto}
\end{figure*}
\end{remark}
%then we reach to a physical page addr (e.g. \textsf{pa}) 
%\[  \paddr\mapsto_{\textsf{a}}\{1\}\vsome \ast \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfrac\naddr \]
  \subsection{Aliasing/Sharing Physical Pages}
\label{sec:sharingpages}
As we see in Figure \fref{fig:}, virtual address mapping is obtained simply in two fold: 1. traversing the page tables to reach the page table entry 2. fetch the physical address and the value it is adressing (Section \ref{fig:physicalpointsto}). This two fold access pattern enabling sharing of pages by virtual memory addresses exhibits logically sound representation against virtual memory operations some of which ((e.g. mapping a new page) we explain in detail in Section \ref{}.

The very first assurance our logical constructions need to be able assert is the \textit{existence} of the page table walk. A naive attempt to assert the existence of the page-walk for a certain virtual memory translation would look like the one in Figure \ref{figure:strongvirtualpointsto}, in which we see that a virtual address with a certain fractional permissions at each level of the page-table walk gives us sound assurance of the path existence reaching to a page table entry, consequently, with a full-ownership of page address, we can obtain and update the value mapped value at this physical page address through our virtual memory address.

>>>>

    \[ \textsf{L4translate} \stackrel{\triangle}{=} \exists \entryf \ldotp \nfpointsto{\mask\vaddr\ft\crthree}{\mask\vaddr\tw\crthree}\entryf\qfracfotsss\naddr \]

@@

    \[ \textsf{L3translate} \stackrel{\triangle}{=} \exists \entrytr \ldotp \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qfracfotss\naddr \]

@@

    \[ \textsf{L2translate} \stackrel{\triangle}{=} \exists \entrytw \ldotp \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qfracfots\naddr \]

@@

    \[ \textsf{L1translate}  \stackrel{\triangle}{=} \exists \entryo \ldotp \nfpointsto{\mask\vaddr\ft\entrytw}{\mask\vaddr\tw\entrytw}\entryo\qfracfot\naddr \]

@@

    \[ \textsf{PageAccess} \stackrel{\triangle}{=} \exists \vpage \ldotp \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr \]

\end{itemize}
\begin{remark}[A Strong Definition for Virtual Memory Addressing]
  \label{rem:strongvmem}
  One could give a naive logical definition to the virtual mememory addressing as conjuctions of each level translation (Figure \fref{fig:strongvirtualpointsto}). The very first assurance our logical constructions need to be able assert is the \textit{existence} of the page table walk. Our naive attempt shown in Figure \ref{figure:strongvirtualpointsto}, we see that a virtual address with a certain fractional permissions at each level of the page-table walk gives us sound assurance of the path existence reaching to a page table entry, consequently, with a full-ownership of page address, we can obtain and update the value mapped value at this physical page address through our virtual memory address.

\begin{figure*}
\[
\begin{array}{l}
  \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage \stackrel{def}{=} \lambda \crthree.\\
  \exists_{\entryf \;, \entrytr \;, \entrytw \;,\entryo} \ldotp

  \ulcorner \textsf{aligned } \vaddr \urcorner \star  \\
  \nfpointsto{\mask\vaddr\ft\crthree}{\mask\vaddr\tw\crthree}\entryf\qfracfotsss\naddr \star \\ 
   \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qfracfotss\naddr  \star  \\
   \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qfracfots\naddr \star \\
  \nfpointsto{\mask\vaddr\ft\entrytw}{\mask\vaddr\tw\entrytw}\entryo\qfracfot\naddr \star \\
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr 
\end{array}
\]
\caption{A Strong Virtual Points-to Relation}
\todo[inline]{These fractions aren't quite right (though I see you added the variance between levels), I can walk you through in our meeting tomorrow.}
  \label{fig:strongvirtualpointsto}
\end{figure*}
\end{remark}
%then we reach to a physical page addr (e.g. \textsf{pa}) 
%\[  \paddr\mapsto_{\textsf{a}}\{1\}\vsome \ast \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfrac\naddr \]
  \subsection{Aliasing/Sharing Physical Pages}
  \label{sec:sharingpages}
  Here we see that virtual address mapping is obtained simply in two fold: 1. traversing the page tables to reach the page table entry 2. fetch the physical address and the value it is adressing (Section \ref{fig:physicalpointsto}). This two fold access-pattern enabling sharing of pages by virtual memory addresses exhibits logically sound representation against virtual memory operations some of which ((e.g. mapping a new page) we explain in detail in Section \ref{}.
